Supporting Information

### 2018-03-05 SupportingInformation.Rmd
just a comment on what to do next
completed but have not yet fully tested the changes that do a graphical version of the nonparametric tail dependence stuff for C and N data

#utility function
calcstats<-function(v,f,nm)
{
  #calculate the stats
  res<-c(f(v[,1],v[,2],0,.5),
          f(v[,1],v[,2],0.5,1),
          f(v[,1],v[,2],0,.25),
          f(v[,1],v[,2],0.25,.5),
          f(v[,1],v[,2],.5,.75),
          f(v[,1],v[,2],.75,1))
  for (lbd in seq(from=0,to=0.9,by=0.1))
  {
    res<-c(res,f(v[,1],v[,2],lbd,lbd+.1))
  }

  #name the result vector
  h<-paste(nm,c(0,0.5,0,0.25,0.5,0.75,seq(from=0,to=0.9,by=0.1)),"to",
                    c(0.5,1,0.25,0.5,0.75,1,seq(from=0,to=0.9,by=0.1)+.1),sep='')
  h<-gsub(".","p",h,fixed=T)
  names(res)<-h

@@

#now work with the correlation stats
corstats_d<-calcstats(v_CN,Corbds,"Cor")
corstats_K<-apply(FUN=calcstats,X=surv_K,MARGIN=3,f=Corbds,nm="Cor")
corstats_K<-apply(FUN=quantile,X=corstats_K,MARGIN=1,prob=c(.005,0.25,.975,.995))
corstats_S<-apply(FUN=calcstats,X=surv_S,MARGIN=3,f=Corbds,nm="Cor")
corstats_S<-apply(FUN=quantile,X=corstats_S,MARGIN=1,prob=c(.005,0.25,.975,.995))

#now work with the D2 stats
D2stats_d<-calcstats(v_CN,D2bds,"Dtwo")
D2stats_K<-apply(FUN=calcstats,X=surv_K,MARGIN=3,f=D2bds,nm="Dtwo")
D2stats_K<-apply(FUN=quantile,X=D2stats_K,MARGIN=1,prob=c(.005,0.25,.975,.995))
D2stats_S<-apply(FUN=calcstats,X=surv_S,MARGIN=3,f=D2bds,nm="Dtwo")
D2stats_S<-apply(FUN=quantile,X=D2stats_S,MARGIN=1,prob=c(.005,0.25,.975,.995))

#now work with the P stats
Pbds_wrap<-function(vi,vj,lb,ub)
{
  return(Pbds(vi,vj,lb,ub)$abs_res)
}
Pstats_d<-calcstats(v_CN,Pbds_wrap,"P")
Pstats_K<-apply(FUN=calcstats,X=surv_K,MARGIN=3,f=Pbds_wrap,nm="P")
Pstats_S<-apply(FUN=calcstats,X=surv_S,MARGIN=3,f=Pbds_wrap,nm="P")
```

>>>>

#utility function for calculating all the stats we want
calcstats<-function(v,f,nm)
{
  #calculate the stats
  res<-c()
  #f(v[,1],v[,2],0,.5),
  #        f(v[,1],v[,2],0.5,1),
  #        f(v[,1],v[,2],0,.25),
  #        f(v[,1],v[,2],0.25,.5),
  #        f(v[,1],v[,2],.5,.75),
  #        f(v[,1],v[,2],.75,1))
  for (lbd in seq(from=0,to=0.9,by=0.1))
  {
    res<-c(res,f(v[,1],v[,2],lbd,lbd+.1))
  }

  #name the result vector
#  h<-paste(nm,c(0,0.5,0,0.25,0.5,0.75,seq(from=0,to=0.9,by=0.1)),"to",
#                    c(0.5,1,0.25,0.5,0.75,1,seq(from=0,to=0.9,by=0.1)+.1),sep='')
  h<-paste(nm,c(seq(from=0,to=0.9,by=0.1)),"to",
                    c(seq(from=0,to=0.9,by=0.1)+.1),sep='')
  h<-gsub(".","p",h,fixed=T)
  names(res)<-h

@@

#utility function for calculating fractions of surrogates 
#with a stat smaller than that of data, i.e., fraction of 
#surrogates for which the stat value on the data is bigger
fracwork<-function(dvals,surrvals)
{
  frac<-NA*numeric(length(corstats_d))
  names(frac)<-names(dvals)
  for (counter in 1:length(frac))
  {
    frac[counter]<-sum(surrvals[counter,]<dvals[counter])
  }
  return(frac)
}

#now work with the correlation stats
corstats_d<-calcstats(v_CN,Corbds,"Cor")

corstats_K<-apply(FUN=calcstats,X=surv_K,MARGIN=3,f=Corbds,nm="Cor")
corstats_frac_K<-fracwork(corstats_d,corstats_K)
corstats_K<-apply(FUN=quantile,X=corstats_K,MARGIN=1,prob=c(.005,0.25,.975,.995))

corstats_S<-apply(FUN=calcstats,X=surv_S,MARGIN=3,f=Corbds,nm="Cor")
corstats_frac_S<-fracwork(corstats_d,corstats_S)
corstats_S<-apply(FUN=quantile,X=corstats_S,MARGIN=1,prob=c(.005,0.25,.975,.995))

#now work with the D2 stats
D2stats_d<-calcstats(v_CN,D2bds,"Dtwo")

D2stats_K<-apply(FUN=calcstats,X=surv_K,MARGIN=3,f=D2bds,nm="Dtwo")
D2stats_frac_K<-fracwork(D2stats_d,D2stats_K)
D2stats_K<-apply(FUN=quantile,X=D2stats_K,MARGIN=1,prob=c(.005,0.25,.975,.995))

D2stats_S<-apply(FUN=calcstats,X=surv_S,MARGIN=3,f=D2bds,nm="Dtwo")
D2stats_frac_S<-fracwork(D2stats_d,D2stats_S)
D2stats_S<-apply(FUN=quantile,X=D2stats_S,MARGIN=1,prob=c(.005,0.25,.975,.995))

#now work with the P stats
Pbds_wrap<-function(vi,vj,lb,ub)
{
  return(Pbds(vi,vj,lb,ub)$abs_res)
}

Pstats_d<-calcstats(v_CN,Pbds_wrap,"P")

Pstats_K<-apply(FUN=calcstats,X=surv_K,MARGIN=3,f=Pbds_wrap,nm="P")
Pstats_frac_K<-fracwork(Pstats_d,Pstats_K)
Pstats_K<-apply(FUN=quantile,X=Pstats_K,MARGIN=1,prob=c(.005,0.25,.975,.995))

Pstats_S<-apply(FUN=calcstats,X=surv_S,MARGIN=3,f=Pbds_wrap,nm="P")
Pstats_frac_S<-fracwork(Pstats_d,Pstats_S)
Pstats_S<-apply(FUN=quantile,X=Pstats_S,MARGIN=1,prob=c(.005,0.25,.975,.995))
```

<!--Now do the plotting-->
```{r plot_soilCN_graphic_approach, echo=F}
x<-seq(from=0.05,to=0.95,by=0.1)
xlimits<-c(0,1)

#plotting layout, units inches
xht<-0.5
ywd<-0.5
titleht<-.25
panht<-1.5
panwd<-3
gap<-.05
totwd<-ywd+2*panwd+2*gap
totht<-xht+3*panht+3*gap+titleht
pdf(file="CNdata_NonparamTailDep.pdf",width=totwd,height=totht)

#plot kendall results on the left panels, spearman on right,
#cor in top panels, then D2, then P on bottom panels

#kendall, cor
par(fig=c(ywd/totwd,
          (ywd+panwd)/totwd,
          (xht+2*panht+2*gap)/totht,
          (xht+3*panht+2*gap)/totht),
    mai=c(0,0,0,0),mgp=c(3,.15,0),tcl=-.25)
ylimits_cor<-range(corstats_d,corstats_K,corstats_K)
ylimits_cor[2]<-ylimits_cor[2]+.3*diff(ylimits_cor)
plot(x,corstats_d,type='l',col="red",xlim=xlimits,ylim=ylimits_cor,
     xaxt='n')
mtext(side=3,line=0,text="Kendall-preserving surrogates")
mtext(side=2,line=1,text="Partial correlation")
axis(side=1,labels=F)
lines(x,corstats_K[1,],type='l',lty='dotted')
lines(x,corstats_K[2,],type='l',lty='dashed')
lines(x,corstats_K[3,],type='l',lty='dashed')
lines(x,corstats_K[4,],type='l',lty='dotted')
text(xlimits[1],ylimits_cor[1],labels='A',cex=1.5,adj=c(.5,0))
fracplot<-function(fracs,ylims)
{
  for (counter in 1:length(fracs))
  {
    ptxt<-''
    if (fracs[counter]>.975*numsurrog)
    {
      ptxt<-paste(">",fracs[counter],sep='')
    } 
    if (fracs[counter]<.025*numsurrog)
    {
      ptxt<-paste("<",numsurrog-fracs[counter],sep='')
    }
    yht<-ylims[2]-.1*diff(ylims)
    text(x[counter],yht,ptxt,adj=c(0.5,.5),cex=0.5,srt=90)
  }
}
fracplot(corstats_frac_K,ylimits_cor)
vlineplot<-function(x,ylims)
{
  for (counter in 1:length(x))
  {
    lines(rep(x[counter]-(x[2]-x[1])/2,2),ylims,type='l',lty='dotted')
  }
  lines(rep(x[length(x)]+(x[2]-x[1])/2,2),ylims,type='l',lty='dotted')
}
vlineplot(x,ylimits_cor)

#spearman, cor
par(fig=c((ywd+panwd+gap)/totwd,
          (ywd+2*panwd+gap)/totwd,
          (xht+2*panht+2*gap)/totht,
          (xht+3*panht+2*gap)/totht),
    mai=c(0,0,0,0),mgp=c(3,.15,0),tcl=-.25,new=T)
plot(x,corstats_d,type='l',col="red",xlim=xlimits,ylim=ylimits_cor,
     xaxt='n',yaxt='n')
mtext(side=3,line=0,text="Spearman-preserving surrogates")
axis(side=1,labels=F)
axis(side=2,labels=F)
lines(x,corstats_S[1,],type='l',lty='dotted')
lines(x,corstats_S[2,],type='l',lty='dashed')
lines(x,corstats_S[3,],type='l',lty='dashed')
lines(x,corstats_S[4,],type='l',lty='dotted')
text(xlimits[1],ylimits_cor[1],labels='B',cex=1.5,adj=c(.5,0))
fracplot(corstats_frac_S,ylimits_cor)
vlineplot(x,ylimits_cor)

#kendall, D2
par(fig=c(ywd/totwd,
          (ywd+panwd)/totwd,
          (xht+panht+gap)/totht,
          (xht+2*panht+gap)/totht),
    mai=c(0,0,0,0),mgp=c(3,.15,0),tcl=-.25,new=T)
ylimits_D2<-range(D2stats_d,D2stats_K,D2stats_K)
ylimits_D2[2]<-ylimits_D2[2]+.3*diff(ylimits_D2)
plot(x,D2stats_d,type='l',col="red",xlim=xlimits,ylim=ylimits_D2,
     xaxt='n')
mtext(side=2,line=1,text=expression(D[2]))
axis(side=1,labels=F)
lines(x,D2stats_K[1,],type='l',lty='dotted')
lines(x,D2stats_K[2,],type='l',lty='dashed')
lines(x,D2stats_K[3,],type='l',lty='dashed')
lines(x,D2stats_K[4,],type='l',lty='dotted')
text(xlimits[1],ylimits_D2[1],labels='C',cex=1.5,adj=c(.5,0))
fracplot(D2stats_frac_K,ylimits_D2)
vlineplot(x,ylimits_D2)

#spearman, D2
par(fig=c((ywd+panwd+gap)/totwd,
          (ywd+2*panwd+gap)/totwd,
          (xht+panht+gap)/totht,
          (xht+2*panht+gap)/totht),
    mai=c(0,0,0,0),mgp=c(3,.15,0),tcl=-.25,new=T)
plot(x,D2stats_d,type='l',col="red",xlim=xlimits,ylim=ylimits_D2,
     xaxt='n',yaxt='n')
axis(side=1,labels=F)
axis(side=2,labels=F)
lines(x,D2stats_S[1,],type='l',lty='dotted')
lines(x,D2stats_S[2,],type='l',lty='dashed')
lines(x,D2stats_S[3,],type='l',lty='dashed')
lines(x,D2stats_S[4,],type='l',lty='dotted')
text(xlimits[1],ylimits_D2[1],labels='D',cex=1.5,adj=c(.5,0))
fracplot(D2stats_frac_S,ylimits_D2)
vlineplot(x,ylimits_D2)

#kendall, P
par(fig=c(ywd/totwd,
          (ywd+panwd)/totwd,
          (xht)/totht,
          (xht+panht)/totht),
    mai=c(0,0,0,0),mgp=c(3,.15,0),tcl=-.25,new=T)
ylimits_P<-range(Pstats_d,Pstats_K,Pstats_K)
ylimits_P[2]<-ylimits_P[2]+.3*diff(ylimits_P)
plot(x,Pstats_d,type='l',col="red",xlim=xlimits,ylim=ylimits_P)
mtext(side=2,line=1,text="P")
mtext(side=1,line=1,text="Diagonal slice")
lines(x,Pstats_K[1,],type='l',lty='dotted')
lines(x,Pstats_K[2,],type='l',lty='dashed')
lines(x,Pstats_K[3,],type='l',lty='dashed')
lines(x,Pstats_K[4,],type='l',lty='dotted')
text(xlimits[1],ylimits_P[1],labels='E',cex=1.5,adj=c(.5,0))
fracplot(Pstats_frac_K,ylimits_P)
vlineplot(x,ylimits_P)

#spearman, P
par(fig=c((ywd+panwd+gap)/totwd,
          (ywd+2*panwd+gap)/totwd,
          (xht)/totht,
          (xht+panht)/totht),
    mai=c(0,0,0,0),mgp=c(3,.15,0),tcl=-.25,new=T)
plot(x,Pstats_d,type='l',col="red",xlim=xlimits,ylim=ylimits_P,
     yaxt='n')
mtext(side=1,line=1,text="Diagonal slice")
axis(side=2,labels=F)
lines(x,Pstats_S[1,],type='l',lty='dotted')
lines(x,Pstats_S[2,],type='l',lty='dashed')
lines(x,Pstats_S[3,],type='l',lty='dashed')
lines(x,Pstats_S[4,],type='l',lty='dotted')
text(xlimits[1],ylimits_P[1],labels='F',cex=1.5,adj=c(.5,0))
fracplot(Pstats_frac_S,ylimits_P)
vlineplot(x,ylimits_P)

dev.off()
